[dcpo_demsupport]

### 2020-08-08 paper/dcpo_demsupport.Rmd
including sigma in 1--4

mod_ls <- paste0(
  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
)

@@

mod_ls <- paste0(
  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)",
    " | plm::lag(Vdem_libdem, 3:5)"
)

@@

df_result_dcpo[4] <- map(mod_ls[[2]], estimate_dcpo, aType = "gmm")

>>>>

mod_ls <- paste0(
  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(sigma, 1) + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
)

@@

mod_ls <- paste0(
  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(sigma, 1) + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)",
    " | plm::lag(Vdem_libdem, 3:5)"
)

@@

# df_result_dcpo[4] <- map(mod_ls[[2]], estimate_dcpo, aType = "gmm")
